Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-08 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{blue}{Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system. Therefore, our technique produces an optimization.}

>>>>

\textcolor{blue}{In summary, our proposal is a technique based on CEGIS, which aims to synthesize the optimal solution of a PV system; therefore, our technique addresses an optimization problem.}

### 2020-07-08 Tex/CAV2019/replyVSTTEJUNE2020.tex
revised paper and letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
We thank the reviewer again for this insightful comment. We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, and Background sections). Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification. We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization). We expect that the revised sections below can clarify the issue, besides the next answer related to Algorithm 1.

Into the Abstract section now we have: "Here we develop and evaluate an automated synthesis technique to obtain optimal sizing of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization."

In the Background section now we have: "Summarizing: Our proposal is a technique based on CEGIS and we aim to synthesize the optimal solution of a PV system. Therefore, our technique produces an optimization."

\textcolor{red}{The two above sentences are new}.

\end{resposta}

>>>>

\begin{resposta} 
We thank the reviewer again for this insightful comment. We had to revise some specific parts of the paper, where the CEGIS technique or optimization appeared (Abstract and Background sections). Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification. We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization). We expect that the revised sections below clarify the issue, besides the next answer related to Algorithm 1.

In the Abstract section, we now have: ``Here we develop and evaluate an automated synthesis technique to obtain optimal sizing of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement, operation, and maintenance costs over $20$ years. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the PV sizing optimization.''

In the Background section, we now have: ``In summary, our proposal is a technique based on CEGIS, which aims to synthesize the optimal solution of a PV system; therefore, our technique addresses an optimization problem.''
\end{resposta}
